---
title: "Selection Review - Overview"
author: "Triet Do"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  echo = FALSE)

options(encoding = 'UTF-8')

# Standalone Report - Disable when execute file
# source("ini.R")
# Today <- Sys.Date() - days(1)
# source("get_data.R")
# ReviewRegion <- "SOUTH"
# ReviewCateReport <- c("FRESH")
# FreshCategory <- CleanSelection %>%
#   select(Cate2Id, Cate2, TikingonCateReport) %>%
#   distinct(Cate2Id, .keep_all = TRUE) %>%
#   filter(TikingonCateReport == 'FRESH')
# 
# FmcgCategory <- CleanSelection %>%
#   select(Cate2Id, Cate2, TikingonCateReport) %>%
#   distinct(Cate2Id, .keep_all = TRUE) %>%
#   filter(TikingonCateReport %in% c('FMCG', 'NON-FOOD'))

#ReviewCategory <- c("Thịt, Trứng", "Cá, thuỷ hải sản", "Rau củ quả", "Trái cây", "Thực phẩm Việt", "Thực Phẩm Chế Biến Sẵn", "Đông lạnh, mát", "Thực phẩm chay")
# ReviewCategory <- c("Sữa, bơ, phô mai", "Dầu ăn, gia vị", "Bia, đồ uống", "Bánh kẹo, giỏ quà", "Đồ hộp, đóng gói", "Gạo, mì, nông sản", "Dành cho trẻ em", "Thức ăn, đồ thú cưng", "Chăm sóc cá nhân", "Chăm sóc nhà cửa", "Gia dụng, tiện ích")
```
# GLOSSARY

## SKU Classification
**SKU A**: SKUs accumlating up to 80% of analyzing period's NMV

**SKU B**: SKUs accumlating up to 95% of analyzing period's NMV

**SKU C**: SKUs accumlating up to 100% of analyzing period's NMV

**SKU D**: SKU contributing no sales in the analyzing period's NMV

## Active SKU
**Active SKUs** wihin a period is any SKU which:
- Has available stock
- Generates sales
- Has shrinkage.

# OVERVIEW FOR TOTAL NGON

## Margins

Front Margin will be calculated based on the following formular:

$$\begin{eqnarray}
FrontMargin &=& \frac{ProductSellingValue - ProductBuyingValue}{ProductSellingValue} \\\\ &=& \frac{\sum{SellingPrice*Qty} - \sum{COGS*Qty}}{\sum{SellingPrice*Qty}}
\end{eqnarray}$$

### Month To Date - Margin - Total Ngon Sub-category

```{r}
ReviewPeriod <- "MidTerm"

StartDate <- as.Date(ISOdate(year(Today), month(Today), 1))
EndDate <- as.Date(Today  - days(1))
source("get_period_data.R")
```

Margins are calculated based on sales and inventory data from `r StartDate` to `r EndDate`

```{r}
SkuMargin <- TotalSummary %>%
  # filter(CustomerGroupRegion == ReviewRegion,
  #        TikingonCateReport %in% ReviewCateReport) %>%
  mutate(SellingValue = SkuValue,
         BuyingValue = Cogs*NmvQty) %>%
  mutate_if(is.numeric, na.fill, 0) %>%
  # CASH HOLDING COST
  group_by(Sku, ProductName, Cate2Id, Cate2, TikingonCateReport) %>%
  summarize(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            ShrinkageValue = sum(ShrinkageValue),
            SkuNmv = sum(SkuNmv),
            CashHoldingCost = mean(QtyInventorySalable*Cogs*WACC)) %>%
  ungroup()

TotalMargin <- SkuMargin %>%
  summarise(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            CashHoldingCost = sum(CashHoldingCost),
            ShrinkageValue = sum(ShrinkageValue),
            FrontMargin = (SellingValue - BuyingValue)/SellingValue,
            RefinedFrontMargin = (SellingValue - BuyingValue - CashHoldingCost - ShrinkageValue)/SellingValue,
            Nmv = sum(SkuNmv)) %>%
  mutate(TikingonCateReport = 'Total Ngon') %>%
  select(TikingonCateReport, Nmv, FrontMargin, RefinedFrontMargin)

NgonSubcateMargin <- SkuMargin %>%
  group_by(TikingonCateReport) %>%
  summarise(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            CashHoldingCost = sum(CashHoldingCost),
            ShrinkageValue = sum(ShrinkageValue),
            FrontMargin = (SellingValue - BuyingValue)/SellingValue,
            RefinedFrontMargin = (SellingValue - BuyingValue - CashHoldingCost - ShrinkageValue)/SellingValue,
            Nmv = sum(SkuNmv)) %>%
  ungroup() %>%
  select(TikingonCateReport, Nmv, FrontMargin, RefinedFrontMargin) %>%
  bind_rows(TotalMargin)

FormatSummaryTable(NgonSubcateMargin, percentageColNames = c('FrontMargin', 'RefinedFrontMargin'))
```

### Last Month - Margin - Total Ngon Sub-category

```{r}
ReviewPeriod <- "MidTerm"

StartDate <- as.Date(ISOdate(year(Today), month(Today), 1) - months(1))
EndDate <- as.Date(ISOdate(year(Today), month(Today), 1)  - days(1))
source("get_period_data.R")
```

Margins are calculated based on sales and inventory data from `r StartDate` to `r EndDate`

```{r}
SkuMargin <- TotalSummary %>%
  # filter(CustomerGroupRegion == ReviewRegion,
  #        TikingonCateReport %in% ReviewCateReport) %>%
  mutate(SellingValue = SkuValue,
         BuyingValue = Cogs*NmvQty) %>%
  mutate_if(is.numeric, na.fill, 0) %>%
  # CASH HOLDING COST
  group_by(Sku, ProductName, Cate2Id, Cate2, TikingonCateReport) %>%
  summarize(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            ShrinkageValue = sum(ShrinkageValue),
            SkuNmv = sum(SkuNmv),
            CashHoldingCost = mean(QtyInventorySalable*Cogs*WACC)) %>%
  ungroup()

TotalMargin <- SkuMargin %>%
  summarise(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            CashHoldingCost = sum(CashHoldingCost),
            ShrinkageValue = sum(ShrinkageValue),
            FrontMargin = (SellingValue - BuyingValue)/SellingValue,
            RefinedFrontMargin = (SellingValue - BuyingValue - CashHoldingCost - ShrinkageValue)/SellingValue,
            Nmv = sum(SkuNmv)) %>%
  mutate(TikingonCateReport = 'Total Ngon') %>%
  select(TikingonCateReport, Nmv, FrontMargin, RefinedFrontMargin)

NgonSubcateMargin <- SkuMargin %>%
  group_by(TikingonCateReport) %>%
  summarise(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            CashHoldingCost = sum(CashHoldingCost),
            ShrinkageValue = sum(ShrinkageValue),
            FrontMargin = (SellingValue - BuyingValue)/SellingValue,
            RefinedFrontMargin = (SellingValue - BuyingValue - CashHoldingCost - ShrinkageValue)/SellingValue,
            Nmv = sum(SkuNmv)) %>%
  ungroup() %>%
  select(TikingonCateReport, Nmv, FrontMargin, RefinedFrontMargin) %>%
  bind_rows(TotalMargin)

FormatSummaryTable(NgonSubcateMargin, percentageColNames = c('FrontMargin', 'RefinedFrontMargin'))
```

## Out-of-Stock Analysis

```{r}

CleanSelection <- SelectionNgon %>%
  clean_names("upper_camel")

CleanSalesOrder <- RawSalesOrder %>%
  filter(as.Date(order_date) >= StartDate,
         as.Date(order_date) <= EndDate) %>%
  filter(warehouse_name !='DN') %>%
  clean_names("upper_camel")

CleanInv <- NewestCogs %>%
  filter(as.Date(date_key) >= StartDate,
         as.Date(date_key) <= EndDate) %>%
  mutate(warehouse = case_when(
    warehouse == "SGN" ~ "MFTBI",
    warehouse == "HN5" ~ "MFLBI",
    TRUE ~ warehouse
  )) %>%
  filter(!(warehouse %in% c("SGN3", "VLN", "HN4"))) %>%
  filter(warehouse!='DN') %>%
  clean_names("upper_camel")

DaysActive <- nrow(CleanInv %>% distinct(DateKey))

ActiveSkuList <- CleanSalesOrder %>%
  distinct(Sku)
```

```{r}

InvSummary <- CleanInv %>%
  filter(Sku %in% ActiveSkuList$Sku,
         QtyInventorySalable > 0) %>%
  group_by(Sku, Warehouse) %>%
  summarise(AvgStock = mean(QtyInventorySalable),
            StockAvailableDays = n()) %>%
  ungroup() %>%
  mutate(DaysActive = DaysActive,
         OosDays = DaysActive - StockAvailableDays)

SalesSummary <- CleanSalesOrder %>%
  group_by(Sku, WarehouseName) %>%
  summarise(TotalNmv = sum(Nmv),
            TotalNmvQty = sum(ProductQty)) %>%
  ungroup()

OosAnalysis <- InvSummary %>%
  left_join(SalesSummary, by = c("Sku", "Warehouse" = "WarehouseName")) %>%
  mutate_if(is.numeric, na.fill, 0) %>%
  mutate(AvgDailySales = TotalNmv/StockAvailableDays) %>%
  left_join(CleanSelection %>% select(Sku, ProductName, Cate2, Cate2Id, TikingonCateReport, IsListed),
            by = "Sku") %>%
  filter(Warehouse!='DN')
```
### Methodology
Average Daily Sales: $$AverageDailySales = \frac{TotalNMV}{ActiveDays}$$

Out of Stock Rate: $$OOS Rate = \frac{\sum(AverageDailySales*OOSDays)}{\sum(AverageDailySales*ReviewPeriodDays)}$$

* OOS Rate describes the NMV opportunity lost due to OOS dates within review period

### OOS Rate by Ngon Sub Cate

```{r}
OosBySubCate <- OosAnalysis %>%
  group_by(TikingonCateReport) %>%
  summarize(OosRate = 100*sum(AvgDailySales*OosDays)/sum(AvgDailySales*DaysActive)) %>%
  ungroup() %>%
  filter(!is.nan(OosRate))

OosBySubCateDrilldownWarehouse <- OosAnalysis %>%
  group_by(TikingonCateReport, Warehouse) %>%
  summarize(OosRate = 100*sum(AvgDailySales*OosDays)/sum(AvgDailySales*DaysActive)) %>%
  ungroup() %>%
  filter(!is.nan(OosRate)) %>%
  group_nest(TikingonCateReport) %>%
  mutate(
    id = TikingonCateReport,
    type = "column",
    name = "OOS Rate",
    # in the drilldown we'll give the mapping via creating the columns
    data = map(data, mutate, name = Warehouse,  y = OosRate),
    data = map(data, list_parse),
    keys = list(keys)
  )

OosBySubCate %>%
  arrange(TikingonCateReport,desc(OosRate)) %>%
  hchart(
    type = "column",
    hcaes(
      x = TikingonCateReport,
      y = OosRate,
      group = TikingonCateReport,
      drilldown = TikingonCateReport),
    showInLegend = TRUE) %>%
  hc_drilldown(allowPointDrilldown = TRUE,
    series = list_parse(OosBySubCateDrilldownWarehouse)) %>%
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>:<br>
                            {point.OosRate:.2f}%<br>") %>%
  hc_xAxis(title = "Category") %>%
  hc_yAxis(title = "Out of Stock Rate (%)", lineWidth = 3, max = 100, min = 0,
           labels = list(format = "{value}%")) %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text = paste0("Out of Stock Rate by Sub Category")) %>%
  hc_subtitle(text = paste0("by Category, from ", StartDate," to ", EndDate))

```


# OVERVIEW FOR `r ReviewRegion`

```{r}
# CATEGORY ANALYSIS
# SKU COUNT
LatestSelectionSummary <- CleanSelection %>%
  filter(IsSalable == TRUE) %>%
  distinct(Sku, .keep_all = TRUE) %>%
  group_by(Cate2, TikingonCateReport) %>%
  summarize(SkuCount = n()) %>%
  ungroup() %>%
  filter(TikingonCateReport %in% ReviewCateReport)

TotalSkuCount <- sum(LatestSelectionSummary$SkuCount)

# NMV
ReviewPeriod <- "MidTerm"
StartDate <- DatePeriod(ReviewPeriod)
EndDate <- Sys.Date() - days(1)
source("get_period_data.R")

# export(TotalSummary, "TotalSummary.xlsx")

NmvByCate1Month <- TotalSummary %>%
  filter(TikingonCateReport %in% ReviewCateReport,
         CustomerGroupRegion == ReviewRegion) %>%
  group_by(Cate2, TikingonCateReport) %>%
  summarize(CatNmv = sum(SkuNmv)) %>%
  ungroup()

# SKU PER WAREHOUSE
CurrentStockStatus <- InvData %>%
  filter(DateKey == Today) %>%
  left_join(CleanSelection %>% select(Sku, TikingonCateReport), by = "Sku") %>%
  filter(TikingonCateReport %in% ReviewCateReport) %>%
  filter(QtyInventorySalable >0) %>%
  group_by(WarehouseName) %>%
  summarize(SkuPerWarehouse = n_distinct(Sku)) %>%
  ungroup() %>%
  mutate(WarehouseRegion = case_when(
    WarehouseName %in% ActiveCentralWarehouse ~ 'CENTRAL',
    WarehouseName %in% ActiveNorthWarehouse ~ 'NORTH',
    WarehouseName %in% ActiveSouthWarehouse ~ 'SOUTH',
    TRUE ~ 'TRANSIT'))

```


As of `r Today`, sub-category **`r ReviewCateReport`** has **`r TotalSkuCount`** salable products.

The products within each category are as followed:

```{r}
h1 <- CreatePieChart(LatestSelectionSummary, Cate2, SkuCount) %>%
  hc_plotOptions(pie = list(dataLabels = list(enable = TRUE, 
                                              format = '<b>{point.name}</b> <br>{point.percentage:.1f} %'))) %>%
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_add_theme(SetThemeFontForHighcharter()) %>%
  hc_tooltip(useHTLM = TRUE,
             crosshairs = TRUE, shared = TRUE,
             headerFormat = str_c("", " ", '</b>{point.key}</b><br/>'),
             pointFormat = "Percentage: <b>{point.percentage:.1f}%</b> <br>Count: <b>{point.y}SKU</b>",
             valueDecimals = 0) %>%
  hc_title(text = paste0("Number of SKU - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by Category, from ", StartDate," to ", EndDate))

h2 <- CreatePieChart(NmvByCate1Month, Cate2, CatNmv) %>%
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_add_theme(SetThemeFontForHighcharter()) %>%
  hc_tooltip(useHTLM = TRUE,
             crosshairs = TRUE, shared = TRUE,
             headerFormat = str_c("", " ", '</b>{point.key}</b><br/>'),
             pointFormat = "Percentage: <b>{point.percentage:.1f}%</b> <br>Value: <b>{point.y}VND</b>",
             valueDecimals = 0) %>%
  hc_title(text = paste0("NMV Contribution - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by Category, from ", StartDate," to ", EndDate))

hw_grid(h1, h2)

```
For `r ReviewCateReport`, the number of SKU per warehouse is as followed:

```{r}
hchart(CurrentStockStatus, type = 'column', hcaes(x = WarehouseName, y = SkuPerWarehouse, group = WarehouseRegion), 
       showInLegends = TRUE) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text = paste0("SKU Count - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by Warehouse, as of ", EndDate))
```


# LAST 30 DAYS REVIEW

The SKUs being reviewed in this period are (1) SKUs having available stock, (2) SKUs generating sales and (3) SKUs having shrinkage.

```{r}
ReviewPeriod <- "MidTerm"

StartDate <- DatePeriod(ReviewPeriod)
EndDate <- Sys.Date() - days(1)
source("get_period_data.R")
```

Review period: **`r ReviewPeriod`**

Review region: **`r ReviewRegion`**

Review Cate Report: **`r ReviewCateReport`**

From: **`r StartDate`**

To: **`r EndDate`**

As of `r Today`, sub-category **`r ReviewCateReport`** has **`r TotalSkuCount`** salable products.

```{r}

PerformerRankAllCates <- TotalSummary %>%
  filter(CustomerGroupRegion == ReviewRegion,
         TikingonCateReport %in% ReviewCateReport) %>%
  group_by(Sku, ProductName, Cate2, Cate3) %>%
  summarize(SkuNmv = sum(SkuNmv),
            NmvQty = sum(NmvQty),
            AvgStock = ceiling(mean(QtyInventorySalable)),
            TotalCustomer = sum(TotalCustomer),
            ReturnCustomer = max(ReturnCustomer), # returning customer within 6 months
            ShrinkageQty = sum(ShrinkageQty),
            ShrinkageValue = sum(ShrinkageValue),
            AvgSalesPeriod = SkuNmv/(1+as.numeric(difftime(EndDate,StartDate, units = "day"))),
            AvgRating = max(AvgRating),
            TotalApprovedReview = max(TotalApprovedReview),
            LtThreeStarsCount = min(LtThreeStarsCount),
            ShrinkageRate = ShrinkageQty/NmvQty,
            DoC = max(DoC)) %>%
  ungroup() %>%
  mutate(NmvContribution = SkuNmv/sum(SkuNmv)) %>%
  ABCClassify(SkuNmv, abcRange = c(80, 95)) %>%
  mutate(abcclass = ifelse(NmvContribution == 0, 'D', abcclass)) %>%
  arrange(accpercentage)

TotalSkuCatePeriodCount <- nrow(PerformerRankAllCates)

```

Total SKU Active in this period: **`r TotalSkuCatePeriodCount`**

```{r}
OverviewData <- PerformerRankAllCates %>%
  mutate(abcclass = paste0("SKU Class ", abcclass)) %>%
  group_by(abcclass) %>%
  summarize(SkuCount = n())

h1 <- CreatePieChart(OverviewData,
               colX = abcclass,
               colY = SkuCount) %>% 
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_add_theme(SetThemeFontForHighcharter()) %>%
  hc_tooltip(useHTLM = TRUE,
             crosshairs = TRUE, shared = TRUE,
             headerFormat = str_c("", " ", '</b>{point.key}</b><br/>'),
             pointFormat = "Percentage: <b>{point.percentage:.1f}%</b> <br>Count: <b>{point.y}SKU</b>",
             valueDecimals = 0) %>%
  hc_title(text = paste0("ABC SKU Class Contribution - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by SKU Class, from ", StartDate," to ", EndDate))

h2 <- PerformerRankAllCates %>%
  group_by(Cate2) %>%
  summarise(Nmv = sum(SkuNmv)) %>%
  hchart(type = 'treemap', hcaes(x = Cate2, value = Nmv, color = Nmv)) %>%
  hc_tooltip(crosshairs = TRUE, shared = TRUE,
             headerFormat = str_c("", " ", '</b>{point.key}</b><br/>'),
             valuePrefix = str_c("</b>", "", " "),
             valueSuffix = str_c(" ", "VND", "</b>"),
             valueDecimals = 0) %>%
  hc_title(text = paste0("NMV Contribution - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by Category, from ", StartDate," to ", EndDate))

hw_grid(h1, h2)
```

```{r}
ClassificationSummary <- PerformerRankAllCates %>%
  group_by(Cate2, abcclass) %>%
  summarise(ClassCount = n_distinct(Sku)) %>%
  ungroup() %>%
  spread(key = "abcclass", value = "ClassCount") %>%
  mutate_if(is.numeric, na.fill, 0) %>%
  mutate(TotalSkuCount = A + B + C + D,
         NonPerformingPercent = D/TotalSkuCount) %>%
  select(Cate2, TotalSkuCount, A, B, C, D, NonPerformingPercent)

FormatDataTable(ClassificationSummary, decimalDigits = 0, percentageColNames = "NonPerformingPercent")
```


## Top Performing SKUs

```{r}
TopPerformerAllCates <- PerformerRankAllCates %>%
  filter(abcclass == "A")

ClassACount <- nrow(TopPerformerAllCates)

```

There are `r ClassACount` products contribute to 80% of this period's NMV.

Top 10 SKU with the best NMV contributions are as followed:

```{r}

FormatSummaryTable(TopPerformerAllCates %>% 
                     select(Sku, ProductName, Cate2, Cate3,
                            NmvQty, SkuNmv, NmvContribution, DoC,
                            ShrinkageQty, ShrinkageValue,
                            TotalCustomer, ReturnCustomer,
                            TotalApprovedReview, AvgRating, LtThreeStarsCount) %>%
                     head(10), 
                   decimalDigits = 1,
                   percentageColNames = c("NmvContribution"))


```

## Selection Health

```{r}
ACount <- nrow(PerformerRankAllCates[PerformerRankAllCates$abcclass == 'A',])
BCount <- nrow(PerformerRankAllCates[PerformerRankAllCates$abcclass == 'B',])
CCount <- nrow(PerformerRankAllCates[PerformerRankAllCates$abcclass == 'C',])
DCount <- nrow(PerformerRankAllCates[PerformerRankAllCates$abcclass == 'D',])
  
PerformerRankAllCates %>%
  arrange(desc(SkuNmv)) %>%
  hchart(
    type = "column",
    hcaes(
      x = ProductName,
      y = SkuNmv,
      group = abcclass),
    showInLegend = TRUE) %>%
  hc_add_series(name = "Accumulated Contribution", data = PerformerRankAllCates$accpercentage, 
                type = "line",
                yAxis = 1,
                showInLegends = TRUE,
                color = "#323232") %>%
  hc_xAxis(categories = PerformerRankAllCates$ProductName,
             title = "Product Name") %>%
  hc_yAxis_multiples(list(title = "SKU NMV", 
                          lineWidth = 3, max = 1.01*max(PerformerRankAllCates$SkuNmv), min = 0),
                     list(title = "Accumulated Contribution", 
                          showLastLabel = FALSE, opposite = TRUE, max = 100, min = 0)) %>%
  hc_xAxis(plotBands = list(list(from = -0.5, to = ACount - 0.5, color = "rgba(128, 128, 128, 0.5)",
           label = list(text = paste0("A class <br>", ACount, "Products"))),
      list(from = ACount - 0.5, to = ACount + BCount - 0.5, color = "rgba(128, 128, 128, 0.3)",
           label = list(text = paste0("B class <br>",  BCount, " Products"))),
      list(from = ACount + BCount - 0.5, to = ACount + BCount + CCount, color = "rgba(128, 128, 128, 0.1)",
           label = list(text = paste0("C class <br>",  CCount, " Products"))),
      list(from = ACount + BCount + CCount - 0.5, to = ACount + BCount + CCount + DCount, color = "rgba(255, 16, 49, 0.3)",
           label = list(text = paste0("D class <br>",  DCount, " Products"))))) %>%
  hc_plotOptions(series = list(marker = list(enabled = FALSE))) %>%
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_colors(c( "#CB333B",  "#0074BC", "#FFCC32", "#7A121C", "#F37032", "#193661",
               "#EFC1C4",  "#66ABD6", "#FFE084", "#AF7076", "#F7A984", "#7586A0",
               "#DF8489",  "#004570", "#997A1E", "#490A10", "#91431E", "#0F203A" )) %>%
  hc_title(text = paste0("Selection Health - ABC Analysis ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by SKU Class, from ", StartDate," to ", EndDate))
```

### Segmentation by Positive RFM and 2% NMV Contribution


```{r}
BcgData <- TotalSummary %>%
  filter(CustomerGroupRegion == ReviewRegion,
         TikingonCateReport %in% ReviewCateReport) %>%
  mutate(SellingValue = SkuValue,
         BuyingValue = Cogs*NmvQty) %>%
  mutate_if(is.numeric, na.fill, 0) %>%
  # CASH HOLDING COST
  group_by(Sku, ProductName, Cate2Id, Cate2) %>%
  summarize(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            ShrinkageValue = sum(ShrinkageValue),
            SkuNmv = sum(SkuNmv),
            CashHoldingCost = mean(QtyInventorySalable*Cogs*WACC)) %>%
  ungroup() %>%
  group_by(Cate2, Cate2Id) %>%
  mutate(NmvContribution = SkuNmv/sum(SkuNmv)) %>%
  ungroup() %>%
  mutate(NmvContributionAllCate = SkuNmv/sum(SkuNmv),
         RefinedFrontMargin = (SellingValue - BuyingValue - CashHoldingCost - ShrinkageValue)/SellingValue,
         RefinedFrontMarginPercent = 100*RefinedFrontMargin,
         FrontMargin = (SellingValue - BuyingValue)/SellingValue,
         FrontMarginPercent = 100*FrontMargin)

BcgDataGraph <- BcgData %>%
  filter(!is.na(RefinedFrontMargin),
         !is.infinite(RefinedFrontMargin))

MedianContribution <- median(BcgDataGraph$NmvContribution)
MedianRfm <- median(BcgDataGraph$RefinedFrontMargin)
MedianFm <- median(BcgDataGraph$FrontMargin)

XLine <- 0.02
YLine <- 0

h1 <- BcgDataGraph %>%
  group_by(Cate2Id, Cate2) %>%
  summarize(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            ShrinkageValue = sum(ShrinkageValue),
            NmvContributionAllCate = sum(NmvContributionAllCate),
            CashHoldingCost = sum(CashHoldingCost)) %>%
  ungroup() %>%
  mutate(RefinedFrontMargin = (SellingValue - BuyingValue - CashHoldingCost - ShrinkageValue)/SellingValue,
         RefinedFrontMarginPercent = 100*RefinedFrontMargin)
h1 <- h1 %>%
  hchart(type = "scatter",
         maxSize = 100,
         hcaes(x = NmvContributionAllCate,  
               y = RefinedFrontMargin, 
               # size = SellingValue,
               group = Cate2),
               tooltip = list(pointFormat = "<b>{point.Cate2}</b> <br>
               Refined Front Margin (%): <b>{point.RefinedFrontMarginPercent:,.1f}%</b> <br>
               Selling Value (VND): <b>{point.SellingValue:,.0f}</b> <br>
               Buying Value (VND): <b>{point.BuyingValue:,.0f}</b> <br>
               Cash Holding Cost (VND): <b>{point.CashHoldingCost:,.0f}</b> <br>
               Shrinkage Value (VND): <b>{point.ShrinkageValue:,.0f}</b>" )) %>%
  hc_xAxis(title = list(text = "NMV Contribution",
                        startOnTick = FALSE),
           min = -max(abs(h1$NmvContributionAllCate), na.rm = TRUE)*1.1,
           max = max(abs(h1$NmvContributionAllCate), na.rm = TRUE)*1.1) %>%
  hc_yAxis(title = list(text = "Refined Front Margin",
                        startOnTick = FALSE),
           min = -max(abs(h1$RefinedFrontMargin), na.rm = TRUE)*1.1,
           max = max(abs(h1$RefinedFrontMargin), na.rm = TRUE)*1.1,
           plotLines = list(list(color = 'blue',
                            value = YLine,
                            width = 2))) %>%
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text = paste0("Selection Health - Refined Front Margin Analysis - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by Category, from ", StartDate," to ", EndDate))

h2 <- BcgDataGraph %>%
  group_by(Cate2Id, Cate2) %>%
  summarize(SellingValue = sum(SellingValue),
            BuyingValue = sum(BuyingValue),
            ShrinkageValue = sum(ShrinkageValue),
            NmvContributionAllCate = sum(NmvContributionAllCate),
            CashHoldingCost = sum(CashHoldingCost)) %>%
  ungroup() %>%
  mutate(FrontMargin = (SellingValue - BuyingValue)/SellingValue,
         FrontMarginPercent = 100*FrontMargin)
h2 <- h2 %>%
  hchart(type = "scatter",
         maxSize = 100,
         hcaes(x = NmvContributionAllCate,  
               y = FrontMargin, 
               # size = SellingValue,
               group = Cate2),
               tooltip = list(pointFormat = "<b>{point.Cate2}</b> <br>
               Front Margin (%): <b>{point.FrontMarginPercent:,.1f}%</b> <br>
               Selling Value (VND): <b>{point.SellingValue:,.0f}</b> <br>
               Buying Value (VND): <b>{point.BuyingValue:,.0f}</b> <br>
               Cash Holding Cost (VND): <b>{point.CashHoldingCost:,.0f}</b> <br>
               Shrinkage Value (VND): <b>{point.ShrinkageValue:,.0f}</b>" )) %>%
  hc_xAxis(title = list(text = "NMV Contribution",
                        startOnTick = FALSE),
           min = -max(abs(h2$NmvContributionAllCate), na.rm = TRUE)*1.1,
           max = max(abs(h2$NmvContributionAllCate), na.rm = TRUE)*1.1) %>%
  hc_yAxis(title = list(text = "Front Margin",
                        startOnTick = FALSE),
           min = -max(abs(h2$FrontMargin), na.rm = TRUE)*1.1,
           max = max(abs(h2$FrontMargin), na.rm = TRUE)*1.1,
           plotLines = list(list(color = 'blue',
                            value = YLine,
                            width = 2))) %>%
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text = paste0("Selection Health - Front Margin Analysis - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by Category, from ", StartDate," to ", EndDate))

hw_grid(h1, h2)

h3 <- BcgDataGraph
  #filter(Cate2Id %in% c(54290, 54302)) %>%
h3 <- h3 %>%  
  hchart(type = "scatter",
                           maxSize = 70,
                           hcaes(x = NmvContribution,  
                                 y = RefinedFrontMargin, 
                                 #size = SellingValue,
                                 group = Cate2),
                                 tooltip = list(pointFormat = "<b>{point.ProductName}</b> <br>
                                 Refined Front Margin (%): <b>{point.RefinedFrontMarginPercent:,.1f}%</b> <br>
                                 Product Value (VND): <b>{point.SellingValue:,.0f}</b> <br>
                                 COGS (VND): <b>{point.BuyingValue:,.0f}</b> <br>
                                 Cash Holding Cost (VND): <b>{point.CashHoldingCost:,.0f}</b> <br>
                                 Shrinkage Value (VND): <b>{point.ShrinkageValue:,.0f}</b>" )) %>%
  hc_xAxis(title = list(text = "NMV Contribution in Category"),
           min = -max(abs(h3$NmvContribution), na.rm = TRUE)*1.1,
           max = max(abs(h3$NmvContribution), na.rm = TRUE)*1.1,
           plotLines = list(list(color = 'red',
                                 value = XLine,
                            # value = MedianContribution,
                            width = 2))) %>%
  hc_yAxis(title = list(text = "Refined Front Margin"),
           min = -max(abs(h3$RefinedFrontMargin), na.rm = TRUE)*1.1,
           max = max(abs(h3$RefinedFrontMargin), na.rm = TRUE)*1.1,
           plotLines = list(list(color = 'blue',
                            # value = MedianRfm,
                            value = YLine,
                            width = 2))) %>%
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text = paste0("Selection Health - Refined Front Margin Analysis - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by SKU and Category, from ", StartDate," to ", EndDate))

h4 <- BcgDataGraph
  #filter(Cate2Id %in% c(54290, 54302)) %>%
h4 <- h4 %>%
  hchart(type = "scatter",
                           maxSize = 70,
                           hcaes(x = NmvContribution,  
                                 y = FrontMargin, 
                                 #size = SellingValue,
                                 group = Cate2),
                                 tooltip = list(pointFormat = "<b>{point.ProductName}</b> <br>
                                 Front Margin (%): <b>{point.FrontMarginPercent:,.1f}%</b> <br>
                                 Product Value (VND): <b>{point.SellingValue:,.0f}</b> <br>
                                 COGS (VND): <b>{point.BuyingValue:,.0f}</b> <br>
                                 Cash Holding Cost (VND): <b>{point.CashHoldingCost:,.0f}</b> <br>
                                 Shrinkage Value (VND): <b>{point.ShrinkageValue:,.0f}</b>" )) %>%
  hc_xAxis(title = list(text = "NMV Contribution in Category"),
           min = -max(abs(h4$NmvContribution), na.rm = TRUE)*1.1,
           max = max(abs(h4$NmvContribution), na.rm = TRUE)*1.1,
           plotLines = list(list(color = 'red',
                            # value = MedianContribution,
                            value = XLine,
                            width = 2))) %>%
  hc_yAxis(title = list(text = "Front Margin"),
           min = -max(abs(h4$FrontMargin), na.rm = TRUE)*1.1,
           max = max(abs(h4$FrontMargin), na.rm = TRUE)*1.1,
                      plotLines = list(list(color = 'blue',
                            # value = MedianFm,
                            value = YLine,
                            width = 2))) %>%
  hc_colors(CreateTikiNgonColor()) %>% 
  hc_chart(backgroundColor = '#FCFCFC', zoomType = "xy") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text = paste0("Selection Health - Front Margin Analysis - ", ReviewRegion, " ", ReviewCateReport[[1]])) %>%
  hc_subtitle(text = paste("by SKU and Category, from ", StartDate," to ", EndDate))

hw_grid(h3, h4)

# Mean NMV Contribution: `r MedianContribution`
# 
# Mean Refined Margin: `r MedianRfm`
# 
# Mean Front Margin: `r MedianFm`

  
```


```{r}

SegmentationSummary_bytype <- BcgData %>%
  mutate(Types = case_when(
  (RefinedFrontMargin >= YLine) & (NmvContribution >= XLine) ~ "STAR",
  (RefinedFrontMargin >= YLine) & (NmvContribution < XLine) ~ "QUESTION MARK",
  (RefinedFrontMargin < YLine) & (NmvContribution >= XLine) ~ "CASH COW",
  (RefinedFrontMargin < YLine) & (NmvContribution < XLine) ~ "DOG",
  TRUE ~ "RECHECK")) %>%
  group_by(Types) %>%
  summarise(Count = n(),
            NmvAbsolute = sum(SkuNmv)) %>%
  ungroup() %>%
  mutate(NmvPercent = NmvAbsolute/sum(NmvAbsolute))

FormatSummaryTable(SegmentationSummary_bytype, percentageColNames = c('NmvPercent'))


SegmentationSummary_tmp <- BcgData %>%
  mutate(Types = case_when(
  (RefinedFrontMargin >= YLine) & (NmvContribution >= XLine) ~ "STAR",
  (RefinedFrontMargin >= YLine) & (NmvContribution < XLine) ~ "QUESTION MARK",
  (RefinedFrontMargin < YLine) & (NmvContribution >= XLine) ~ "CASH COW",
  (RefinedFrontMargin < YLine) & (NmvContribution < XLine) ~ "DOG",
  TRUE ~ "RECHECK")) %>%
  group_by(Cate2, Types) %>%
  summarise(Count = n(),
            NmvAbsolute = sum(SkuNmv)) %>%
  ungroup() %>%
  mutate(tempvalue = paste0(Count, '%%', NmvAbsolute)) %>%
  select(-Count, -NmvAbsolute) %>%
  spread(key = "Types", value = "tempvalue", fill = 0) %>%
  clean_names('upper_camel') %>%
  select(-contains('Recheck')) %>%
  separate(col = 'CashCow', into = c('CashCow', 'CashCowNmvAbsolute'), sep = '%%') %>%
  separate(col = 'Dog', into = c('Dog', 'DogNmvAbsolute'), sep = '%%') %>%
  separate(col = 'QuestionMark', into = c('QuestionMark', 'QuestionMarkNmvAbsolute'), sep = '%%') %>%
  separate(col = 'Star', into = c('Star', 'StarNmvAbsolute'), sep = '%%') %>%
  mutate(across(everything(), na.fill, 0)) %>%
  mutate(across(!Cate2, as.numeric)) %>%
  mutate(Total = CashCow + Dog + QuestionMark + Star,
         CC_percent = CashCow/Total,
         D_percent = Dog/Total,
         QM_percent = QuestionMark/Total,
         S_percent = Star/Total) %>%
  select(Cate2, Total,
         Star, StarNmvAbsolute, S_percent,
         CashCow, CashCowNmvAbsolute, CC_percent,
         QuestionMark, QuestionMarkNmvAbsolute, QM_percent,
         Dog, DogNmvAbsolute, D_percent)

FormatSummaryTable(SegmentationSummary_tmp, percentageColNames = c('S_percent', 'CC_percent', 'QM_percent', 'D_percent'))

```


## Keywords Analysis

```{r}
source('keywordanalysis.R')

# GRAPH

# all1 <- wordcloud(words = AllSearchClean$SearchKeyword, freq = AllSearchClean$Count, rot.per=0.35, colors=brewer.pal(8, "Dark2"), max.words = 100)
# all2 <- wordcloud(words = KeyFreqClean$SearchKeyword, freq = KeyFreqClean$Count, rot.per=0.35, colors=brewer.pal(8, "Dark2"), max.words = 100)
# 
# 
# hub1 <- wordcloud(words = HubSearchClean$SearchKeyword, freq = HubSearchClean$Count, rot.per=0.35, colors=brewer.pal(8, "Dark2"), max.words = 100)
# hub2 <- wordcloud(words = HubSearchWords$SearchKeyword, freq = HubSearchWords$Count, rot.per=0.35, colors=brewer.pal(8, "Dark2"), max.words = 100)

```

**Top 100 Keywords - Total Tiki/Affiliated Channel**
Directed from all sources

```{r}
all2 <- wordcloud(words = KeyFreqClean$SearchKeyword, freq = KeyFreqClean$Count, rot.per=0.35, colors=brewer.pal(8, "Dark2"), max.words = 100)
```


**Top 100 Keywords - Ngon Hub**
Only from TikiNgon page

```{r}
hub1 <- wordcloud(words = HubSearchClean$SearchKeyword, freq = HubSearchClean$Count, rot.per=0.35, colors=brewer.pal(8, "Dark2"), max.words = 100)
```



```{r}
# EXPORTING DATA

PerformerRankAllCatesExport <- PerformerRankAllCates
OosAnalysisExport <- OosAnalysis %>%
  select(Sku, ProductName, Cate2, TikingonCateReport, Warehouse,
         DaysActive, StockAvailableDays, OosDays,
         TotalNmv, TotalNmvQty)
BcgDataExport <- BcgData %>%
  mutate(Types = case_when(
  (RefinedFrontMargin >= YLine) & (NmvContribution >= XLine) ~ "STAR",
  (RefinedFrontMargin >= YLine) & (NmvContribution < XLine) ~ "QUESTION MARK",
  (RefinedFrontMargin < YLine) & (NmvContribution >= XLine) ~ "CASH COW",
  (RefinedFrontMargin < YLine) & (NmvContribution < XLine) ~ "DOG",
  TRUE ~ "RECHECK"
  ))
NmvSalesTimeSeriesExport <- TotalSummary %>%
  group_by(OrderDate, Sku, ProductName, Cate2, Cate3, TikingonCateReport) %>%
  summarise(SkuNmv = sum(SkuNmv)) %>%
  ungroup() %>%
  spread(key = "OrderDate", value = "SkuNmv", fill = 0)
QtySalesTimeSeriesExport <- TotalSummary %>%
  group_by(OrderDate, Sku, ProductName, Cate2, Cate3, TikingonCateReport) %>%
  summarise(NmvQty = sum(NmvQty)) %>%
  ungroup() %>%
  spread(key = "OrderDate", value = "NmvQty", fill = 0)

export_dir <- paste0(getwd(),"/OUTPUT/", FolderName)

export(list("raw_data_SKU_ABC" = PerformerRankAllCatesExport,
            "raw_data_SKU_segment" = BcgDataExport,
            "raw_data_OOS" = OosAnalysisExport,
            "raw_sales_nmv" = NmvSalesTimeSeriesExport,
            "raw_sales_qty" = QtySalesTimeSeriesExport),
       paste0(export_dir, "/", "raw_data_",ReviewCateReport[[1]],"_",ReviewRegion, ".xlsx"))
```






